Supplementary Information

### 2020-08-01 doc/manuscript/MEE_manuscript.Rmd
integrate new figures
#47

![**Figure 2 | Example comparison of climate sensitivity derived via traditional methods (**a**) and our approach (**b-f**).** Example is for the sensitivity of 14 species at SCBI (codes given in Table S1) to potential evapotranspiration (PET), identified by both traditional methods and our method to be among the top climate drivers. Panel (**a**) shows a matrix of Pearson correlations between ring- width index and monthly climate variables. Panels (**b-d**) give statistics for time windows tested in *climwin*, where window open and close indicate months prior to current August, and cells across the lower diaganol indicate single-month tests (akin to panel **a**). Panels (**b**) and (**c**) give values of linear and quadratic terms for each time window, and (**d**) gives the $\Delta AIC$ for each. The time window with the minimum $\Delta AIC$ (0-3 months prior to August, or May-Aug; black boxes), was identified as the optimal window. Panel (**e**) shows the correlation of individual-level residuals to PET, with the function fit in *climwin*. Finally, panel (**f**) shows GLS model output, where PET is one of several driver variables (*specify model*). Plotted are responses of species for which PET was identified as a signficant driver in the top model.](tables_figures/climate_figure_sketch.png)

@@

![**Figure 3 | Climate senstivity for all sites.** Columns include the top variables in each grouping, with PET placed in the temperature group if identified as the top variable for both the temperature and cloudiness groups. For each species, relationships are plotted if included in top model. Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD. (THIS FIGURE IS JUST A SKETCH TO SHOW VALENTINE WHAT I HAVE IN MIND.) ](tables_figures/climate_figure2_sketch.png)

>>>>

![**Figure 2 | Example comparison of climate sensitivity derived via traditional methods (**a**) and our approach (**b-f**).** Example is for the sensitivity of 14 species at SCBI (codes given in Table S1) to potential evapotranspiration (PET), identified by both traditional methods and our method to be among the top climate drivers. Panel (**a**) shows a matrix of Pearson correlations between ring- width index and monthly climate variables. Panels (**b-d**) give statistics for time windows tested in *climwin*, where window open and close indicate months prior to current August, and cells across the lower diaganol indicate single-month tests (akin to panel **a**). Panels (**b**) and (**c**) give values of linear and quadratic terms for each time window, and (**d**) gives the $\Delta AIC$ for each. The time window with the minimum $\Delta AIC$ (0-3 months prior to August, or May-Aug; black boxes), was identified as the optimal window. Panel (**e**) shows the correlation of individual-level residuals to PET, with the function fit in *climwin*. Finally, panel (**f**) shows GLS model output, where PET is one of several driver variables (*specify model*). Plotted are responses of species for which PET was identified as a signficant driver in the top model.](tables_figures/quilt_comparison.png)

@@

![**Figure 3 | Climate senstivity for all sites.** Columns include the top variables in each grouping, with PET placed in the temperature group if identified as the top variable for both the temperature and cloudiness groups. For each species, relationships are plotted if included in top model. Vertical grey lines indicate the long-term mean for the climate variable, shading indicates 1 SD. (IN-PREP FIGURE.) ](tables_figures/pre_temp_cld_groups.png)
